D_exp_2

### 2018-08-20 experiments/D_exp_2/writeup/D_exp_2.Rmd
dexp2 now has functioning levy i think

The instructions for this experiment were similar to C_exp_2, except that we changed "fewer than" to "far fewer than": this was because "far fewer than" can have borderline cases whereas "fewer than" cannot have borderline cases.

```{r, echo=FALSE}
instructions_table <- 
  dat %>%
    select(Item, Quantity, Vagueness, Selection, Instruction) %>%
    unique() %>%
    arrange(Item, Quantity, Vagueness, Selection) %>%
    spread(key=Vagueness, value=Instruction)
# kable(instructions_table, format="latex", booktabs = TRUE)
instructions_table %>% 
  kable(align='cccll', caption="Full table of instructions") %>% 
      kable_styling(full_width = F, position = "left", font_size = 11) 
```

@@

```{r}
dat_plot <- summarySEwithin2(dat, measurevar="RT_log", withinvars=c("Vagueness", "Selection", "Item"), idvar="Subject")
```

```{r, "EXP_D_RT_means_plot", fig.width=7, fig.height=3, echo=FALSE}
dodge = position_dodge(width=0.2)
dat_plot$Condition <- as.factor(paste(sep=' ', dat_plot$Selection, dat_plot$Vagueness))
ggplot(dat_plot, aes(y=RT_logNormed, x=Item, ymin=RT_logNormed-ci, ymax=RT_logNormed+ci, group=Condition, shape=Condition, fill=Condition)) +
  geom_line(position=dodge) +
  geom_errorbar(width=.2, position=dodge) +
  geom_point(size=2, position=dodge) +
  scale_shape_manual("",values = c(22, 22, 21, 21)) +
  scale_fill_manual("",values=c("black","white","black","white")) +
  ggtitle("Response time") +
  ylab("Respone time (log (ms))") + 
  xlab("") +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        legend.key = element_blank(), aspect.ratio=1,
        axis.text.x = element_text(angle = 45, hjust = 1),
        plot.background=element_rect(fill=NA, color='white')) +
  facet_grid(~Selection) 
```

```{r, "EXP_D_Borderline_response_distribution_plot", fig.width=7, fig.height=3.5, echo=FALSE}
dat_borderline$response_cat <- factor(dat_borderline$response_cat, levels= c("Near", "Expected", "Far"))
ggplot(dat_borderline) + 
  geom_bar(aes(response_cat, group=Selection:Vagueness, fill=Vagueness), position=position_dodge(width=NULL)) +   
  scale_fill_grey() + 
  xlab(NULL) + 
  ggtitle('Borderline response distribution') + 
  facet_grid(~Selection) +
  theme_bw() + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.key = element_blank(), legend.position="top", aspect.ratio=1, plot.background = element_rect(fill=NA, color='white'), strip.background=element_blank(), legend.key.size=unit(4, 'mm'), axis.text.x = element_text(angle = 15))
```

@@

The second set of models considered were conducted to test for main effects _in the presence of interactions involving those main effects_ (after Levy, 2018)

# Discussion

>>>>

We changed "fewer than" (crisp) to "far fewer than" (in vague): this was because "far fewer than" can have borderline cases whereas "fewer than" cannot have borderline cases.

```{r, echo=FALSE}
instructions_table <- 
  dat %>%
    select(Item, Quantity, Vagueness, Selection, Instruction) %>%
    unique() %>%
    arrange(Item, Quantity, Vagueness, Selection) %>%
    spread(key=Vagueness, value=Instruction)
instructions_table %>% 
  kable(align='cccll', caption="Full table of instructions") %>% 
      kable_styling(full_width = F, position = "left", font_size = 11) 
```

@@

```{r, cho=FALSE}
dat_plot <- summarySEwithin2(dat, measurevar="RT_log", withinvars=c("Vagueness", "Selection", "Item"), idvar="Subject")
```

```{r, "EXP_D_RT_means_plot", fig.width=7, fig.height=3, echo=FALSE}
dodge = position_dodge(width=0.2)
dat_plot$Condition <- as.factor(paste(sep=' ', dat_plot$Selection, dat_plot$Vagueness))
ggplot(dat_plot, aes(y=RT_logNormed, x=Item, ymin=RT_logNormed-ci, ymax=RT_logNormed+ci, group=Condition, shape=Condition, fill=Condition)) +
  geom_line(position=dodge) +
  geom_errorbar(width=.2, position=dodge) +
  geom_point(size=2, position=dodge) +
  scale_shape_manual("",values = c(22, 22, 21, 21)) +
  scale_fill_manual("",values=c("black","white","black","white")) +
  ggtitle("Response time") +
  ylab("Respone time (log (ms))") + 
  xlab("") +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        legend.key = element_blank(), aspect.ratio=1,
        axis.text.x = element_text(angle = 45, hjust = 1),
        plot.background=element_rect(fill=NA, color='white')) +
  facet_grid(~Selection) 
```
```{r, "EXP_D_Borderline_response_distribution_plot", fig.width=7, fig.height=3.5, echo=FALSE}
dat_borderline$response_cat <- factor(dat_borderline$response_cat, levels= c("Near", "Expected", "Far"))
ggplot(dat_borderline) + 
  geom_bar(aes(response_cat, group=Selection:Vagueness, fill=Vagueness), position=position_dodge(width=NULL)) +   
  scale_fill_grey() + 
  xlab(NULL) + 
  ggtitle('Borderline response distribution') + 
  facet_grid(~Selection) +
  theme_bw() + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.key = element_blank(), legend.position="top", aspect.ratio=1, plot.background = element_rect(fill=NA, color='white'), strip.background=element_blank(), legend.key.size=unit(4, 'mm'), axis.text.x = element_text(angle = 15))
```

@@

The second set of models considered were conducted to test for main effects _in the presence of interactions involving those main effects_ (after Levy, 2018).

The variables are:
Vagueness 2 levels (X) sumcoded -.5, +.5 
Item 4 levels (Y) 
Selection 2 levels (Z)

Note that the null-hypothsesis model _includes_ random slopes for the main effect of X; Y; and Z; as well as for their interactions -- including a seperate random slope for all combiations of X, Y, and Z achieves this.

```{r}
dat$XYZ <- with(dat, factor(paste(Vagueness,Item,Selection)))
```

Convert a K level factor Y into a sum-coding representation.

```{r}
Item.numeric <- sapply(dat$Item,function(i) contr.sum(4)[i,])
dat$Item1 <- Item.numeric[1,]
dat$Item2 <- Item.numeric[2,]
dat$Item3 <- Item.numeric[3,]
```

```{r}
dat_model <- dat
Item.numeric <- sapply(dat_model$Item,function(i) contr.sum(4)[i,])
dat_model$Item1 <- Item.numeric[1,]
dat_model$Item2 <- Item.numeric[2,]
dat_model$Item3 <- Item.numeric[3,]
dat_model$c_Sel <- ifelse(dat_model$Selection=="Comparison", -0.5, 0.5)
dat_model$c_Vag <- ifelse(dat_model$Vagueness=="Crisp", -0.5, 0.5)
dat_model$c_Sel <- ifelse(dat_model$Selection=="Comparison", -0.5, 0.5)
dat_model$c_Itm <- ifelse(dat_model$Item=="06:15:24", -.75, ifelse(dat_model$Item=="16:25:34", -.25, ifelse(dat_model$Item=="26:35:44", .25, .75)))

null.model <- lmer(RT_log ~ 
                     Item1 + c_Vag:Item1 +
                     Item2 + c_Vag:Item2 + 
                     Item3 + c_Vag:Item3 + 
                     c_Sel + c_Vag:c_Sel + 
                     (1 + c_Vag * c_Itm * c_Sel|Subject), dat_model, REML=FALSE)
pretty_coef_table(null.model, "null model")

full.model <- lmer(RT_log ~ 
                     Item1 + c_Vag:Item1 +
                     Item2 + c_Vag:Item2 + 
                     Item3 + c_Vag:Item3 + 
                     c_Sel + c_Vag:c_Sel + c_Vag +
                     (1 + c_Vag * c_Itm * c_Sel|Subject), dat_model, REML=FALSE)
pretty_coef_table(full.model, "full model")

anova(null.model, full.model)
```
